Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm} Stagnating State Funding for Higher Education and its Effect on Faculty

### 2024-09-27 text/sections/05-results.tex
This is all done.

\subsection{First-Stage Estimates}
\label{sec:results-firststage}
The shift-share instrument has a strong first-stage for universities' yearly state funding.
\autoref{tab:firststage-reg} show results of the first-stage regression among IPEDS data, separately with and without a control for tuition revenue per student.
\autoref{tab:firststage-reg} Panel A shows estimates of a state funding shift-share of \$1 per student on state funding per student at the university, and Panel B the effects of a 1\% increase in the state funding shift-share on state funding per student.
Column (1) shows that a state funding shift-share of \$10 per student is associated with \$11.76 less state funding per student at the university; $-10$\% state funding shift-share leads to $-9.77$\% state funding per student at the average university.
Estimates are presented for specifications with and without fixed effects.
Column (2) shows estimates of the first-stage without including fixed effects, and gives less precise estimates for the funding shift-share --- this may be due to systematic differences in universities, which are not accounted for when omitting fixed effects.
Columns (3) and (4) include the tuition revenue as a control (explained in \autoref{foot:control}) to exhibit estimates with or without this control variable.
Column (3) shows similar estimates to column (1) in both Panels A and B thanks to inclusion of fixed effects, so whether tuition revenue is a bad control does not affect empirical estimates.
Column (1) represents the estimates for \autoref{eqn:firststage} with fixed effects (not including tuition revenue as a control variable), and is the preferred specification that I proceed with;
all specifications (except column 4 in both panels) have a large F statistic on the excluded instrument.\footnote{
    I calculate the F statistic on the excluded instrument, while also accounting for fixed effects and two-way standard error clustering, by the methods provided in \cite{olea2013robust}.
}
I use the same empirical strategy in the analysis of Illinois faculty, and \autoref{tab:firststage-illinois} presents first-stage estimates among the IBHED data; results are similar to those calculated in IPEDS data.
These results show the funding shift-share instrument strongly predicts a university's state funding in the first-stage estimation.

@@

\subsection{University Level, IPEDS}
\label{sec:results-ipeds}
State funding cuts lead to measurable changes in the number of faculty at US public universities.
\autoref{tab:facultycount-shock-reg} presents OLS and IV estimates for the effect of state funding cuts on the number of faculty at public universities, separately for each faculty position (lecturer, assistant and full professors, total).
The results are presented in two different units: Panel A shows how a \$1 increase in state funding changed the count of faculty per students, while Panel B shows how a 1\% increase in state funding led to a percent change in the number of faculty per students.

An extra \$1,000 in state funding per student leads to the average university employing 6 fewer lecturers, while effects for the other positions are not discernible from zero (\autoref{tab:facultycount-shock-reg}, Panel A).
A 10\% state funding cut lead to a 4.4\% increase in the number of lecturers per student, and a decrease of 1.35\% and 1.37\% for assistant and full professors, respectively.
A state funding cut of 10\% leads to a 0.65\% decrease in the total number of faculty per student (\autoref{tab:facultycount-shock-reg}, Panel B).
These are large substitution effects, and explain roughly 40\% of the trend in substitution towards lecturers over the same time period.
The average public university has roughly 36\% less state funding per student in 2021 than they did in 1990, while employing over double the number of lecturers and 20\% fewer professors (relative to enrolment, seen in \autoref{fig:mean-funding-fte}, \ref{fig:fte-perprof}).

Universities do not re-adjust by hiring more professors to make up for last year's funding cut, and so the substitution towards lecturers becomes persistent.
\autoref{fig:count-lp} shows LP estimates, showing the elasticity for professor count per student in year $t+k$ with respect to state funding in year $t$ (and cumulative intermediate cuts).
State funding cuts affect the number of lecturers and professors at universities up to 9 years after the initial funding cut.
A 10\% state funding cut leads to 4.2\% (2.9--5.5 in a 95 percent confidence interval) more lecturers per student the following year, and around 3.1\% (0.6--5.5 confidence interval) more lecturers nine years later.
A 10\% state funding cut leads to 1.5\% (0.6--2.2 in a 95 percent confidence interval) fewer assistant professors per student the following year, and around 1.1\% (0.2--2.0 confidence interval) fewer nine years later;
the same cut leads to 1.2\% (0.6--1.8 in a 95 percent confidence interval) fewer full professors per student the following year, and around 0.9\% (0.1--1.7 confidence interval) fewer nine years later.

These effects are a substitution of professors for lecturers at public universities, as the total number of faculty per students are relatively unrelated to funding cuts, but the lecturer count increases and professor count decreases.
This agrees with a model for universities departments having fixed teaching requirements making human-resources decisions under constrained resources (e.g., \citealt{abe2015implications}), lending credibility to this type of model for understanding recent human resources decisions of public universities.
Furthermore, if a university must teach more students, but cannot afford to hire a full-time professor who teaches 2--3 classes a year, then it makes sense that they hire 2--3 additional lecturers on part-time contracts for each class as a replacement.
This provides simple intuition for why the lecturers' elasticity is 2--3 times larger than that for assistant/full professors in \autoref{tab:facultycount-shock-reg}.
While no previous research causally connects funding cuts to substituting professors for lecturers, the phenomenon has been alluded to in popular media \citep{wiu2016} and university rankings (where more lecturers hurts a university's ranking, \citealt{usnews2023}).
The results provided here give the first real evidence for such popular claims.

@@

\autoref{tab:facultyhires-illinois-reg} shows these estimates for Illinois public universities.
In general, faculty counts are relatively unrelated to state funding among Illinois universities; though the point estimates line up with analysis in IPEDS, the smaller number of observations mean that the precision of estimates are small and indistinguishable from zero, in both raw counts and in log units.
In the national-level \cite{wapman2022quantifying} data, universities with more state funding hire more professors across 2011--2021.
An extra 10\% in state funding is associated with 8.5\% more professors hired per students, as seen in \autoref{fig:hiring-correlation}.
I use these data as part of a shift-share analysis, showing that a 10\% state funding cut per student leads to 13\% fewer professor hires (relative to enrolment), and that these hires are roughly equal for gender of professor hired.

@@

Last, I investigate when the substitution towards lecturers occurred.
To do so, I estimate the effect of state funding on faculty counts relative student enrolment separately for 1990--2009 and 2010--2021.
Substitution towards lecturer is weak to non existent in the latest decade, as noted in contemporary research \citep{hinrichs2022state}.
However, the rates are stronger when just looking at the years 1990--2010.
This reflects a key point noted in \autoref{sec:trends}: a large amount of the cuts, and general stagnation, in state funding for public universities occurred over in the 1990s and 2000s.
Additionally, the trend in rising lecturer count, and falling full professor count, per student at public universities had been operating all throughout the 1990s and 2000s.
These trends did continue in the 2010s (especially for counts of assistant professors), but most of the substitution had already taken place by this point.

>>>>

\subsection{First-Stage Estimates}
\label{sec:results-firststage}
The shift-share instrument has a strong first-stage for universities' yearly state funding.
\autoref{tab:firststage-reg} show results of the first-stage regression among IPEDS data, separately with and without a control for tuition revenue per student.
\autoref{tab:firststage-reg} Panel A shows estimates of a state funding shift-share of \$1 per student on state funding per student at the university, and Panel B the effects of a 1\% increase in the state funding shift-share on state funding per student.
Column (1) shows that a state funding shift-share of \$10 per student is associated with \$11.76 less state funding per student at the university; $-10$\% state funding shift-share leads to $-9.77$\% state funding per student at the average university.
Estimates are presented for specifications with and without fixed effects.
Column (2) shows estimates of the first-stage without including fixed effects, and gives less precise estimates for the funding shift-share --- this may be due to systematic differences in universities, which are not accounted for when omitting fixed effects.
Columns (3) and (4) include the tuition revenue as a control (explained in \autoref{foot:control}) to exhibit estimates with or without this control variable.
Column (3) shows similar estimates to column (1) in both Panels A and B thanks to inclusion of fixed effects, so whether tuition revenue is a bad control does not affect empirical estimates.
Column (1) represents the estimates for \autoref{eqn:firststage} with fixed effects (not including tuition revenue as a control variable), and is the preferred specification that I proceed with;
all specifications (except column 4 in both panels) have a large F statistic on the excluded instrument.\footnote{
    I calculate the F statistic on the excluded instrument, while also accounting for fixed effects and two-way standard error clustering, by the methods provided in \cite{olea2013robust}.
}
I use the same empirical strategy in the analysis of Illinois faculty, and \autoref{tab:firststage-illinois} presents first-stage estimates among the IBHED data; results are similar to those calculated in IPEDS data.\footnote{
    Every IV specification presented in this paper uses a specification with a strong first-stage.
    Results with weak first-stages are omitted as they would not be reliable causal effects.
}
These results show the funding shift-share instrument strongly predicts a university's state funding in the first-stage estimation.

@@

\subsection{University Level, IPEDS}
\label{sec:results-ipeds}
State funding cuts lead to measurable changes in the number of faculty at US public universities.
\autoref{tab:facultycount-shock-reg} presents OLS and IV estimates for the effect of state funding cuts on the number of faculty at public universities, separately for each faculty position (lecturer, assistant professors and professors, total).
The results are presented in two different units: Panel A shows how a \$1,000 state funding cut per-student changed the count of faculty, while Panel B shows how a 1\% increase in state funding led to a percent change in the number of faculty per students.

An extra \$1,000 in state funding per student leads to the average university employing 6 more lecturers, while effects for the other positions are not discernible from zero (\autoref{tab:facultycount-shock-reg}, Panel A).
A 10\% state funding cut lead to a 4.4\% increase in the number of lecturers per student, and a decrease of 1.35\% and 1.37\% for assistant and professors, respectively.
A state funding cut of 10\% leads to a 0.65\% decrease in the total number of faculty per student (\autoref{tab:facultycount-shock-reg}, Panel B).
These are large substitution effects, and explain roughly 40\% of the trend in substitution towards lecturers over the same time period.
The average public university has roughly 36\% less state funding per student in 2021 than they did in 1990, while employing over double the number of lecturers and 20\% fewer professors (relative to enrolment, seen in \autoref{fig:mean-funding-fte}, \ref{fig:fte-perprof}).

Universities do not re-adjust by hiring more professors to make up for last year's funding cut, and so the substitution towards lecturers becomes persistent.
\autoref{fig:count-lp} shows LP estimates, showing the elasticity for professor count per student in year $t+k$ with respect to state funding in year $t$ (and cumulative intermediate cuts).
State funding cuts affect the number of lecturers and professors at universities up to 9 years after the initial funding cut.
A 10\% state funding cut leads to 4.2\% (2.9--5.5 in a 95 percent confidence interval) more lecturers per student the following year, and around 3.1\% (0.6--5.5 confidence interval) more lecturers nine years later.
A 10\% state funding cut leads to 1.5\% (0.6--2.2 in a 95 percent confidence interval) fewer assistant professors per student the following year, and around 1.1\% (0.2--2.0 confidence interval) fewer nine years later;
the same cut leads to 1.2\% (0.6--1.8 in a 95 percent confidence interval) fewer professors per student the following year, and around 0.9\% (0.1--1.7 confidence interval) fewer nine years later.

These effects are a substitution of professors for lecturers at public universities, as the total number of faculty per students are relatively unrelated to funding cuts, but the lecturer count increases and professor count decreases.
This agrees with a model for universities departments having fixed teaching requirements making human-resources decisions under constrained resources (e.g., \citealt{abe2015implications}), lending credibility to this type of model for understanding recent human resources decisions of public universities.
Furthermore, if a university must teach more students, but cannot afford to hire a full-time professor who teaches 2--3 classes a year, then it makes sense that they hire 2--3 additional lecturers on part-time contracts for each class as a replacement.
This provides simple intuition for why the lecturers' elasticity is 2--3 times larger than that for assistant/professors in \autoref{tab:facultycount-shock-reg}.
While no previous research causally connects funding cuts to substituting professors for lecturers, the phenomenon has been alluded to in popular media \citep{wiu2016} and university rankings (where more lecturers hurts a university's ranking, \citealt{usnews2023}).
The results provided here give the first real evidence for such popular claims.

@@

\autoref{tab:facultyhires-illinois-reg} shows these estimates for Illinois public universities.
In general, faculty counts are relatively unrelated to state funding among Illinois universities; though the point estimates line up with analysis in IPEDS, the smaller number of observations mean that the precision of estimates are small and indistinguishable from zero, in both raw counts and in log units.
In the national-level \cite{wapman2022quantifying} data, universities with more state funding hire more professors across 2011--2021.
An extra 10\% in state funding is associated with 8.5\% more professors hired per students, as seen in \autoref{fig:hiring-correlation}.
I use these data as part of a shift-share analysis, showing that a 10\% state funding cut per student leads to 13\% fewer professor hires (relative to enrolment), and that these hires are roughly equal for gender of professor hired.\footnote{
    However, most of the variation in state funding cuts and substitution towards lecturers happens during the 1990--2009 period.
    So this analysis of 2011--2021 data is not ground-truth evidence for mechanisms over 1990--2009.
}

@@

Last, I investigate when the substitution towards lecturers occurred.
To do so, I estimate the effect of state funding on faculty counts relative student enrolment separately for 1990--2009 and 2010--2021.
Substitution towards lecturer is weak to non existent in the latest decade, as noted in contemporary research \citep{hinrichs2022state}.
However, the rates are stronger when just looking at the years 1990--2010.
This reflects a key point noted in \autoref{sec:trends}: a large amount of the cuts, and general stagnation, in state funding for public universities occurred over in the 1990s and 2000s.
Additionally, the trend in rising lecturer count, and falling professor count, per student at public universities had been operating all throughout the 1990s and 2000s.
These trends did continue in the 2010s (especially for counts of assistant professors), but most of the substitution had already taken place by this point.

### 2024-09-27 text/sections/08-figures-tables.tex
This is all done.

\begin{table}[H]
    \singlespacing
    \centering
    \caption{IBHED Summary Statistics, Faculty Panel 2010--2021.}
    \makebox[\textwidth][c]{\input{tables/illinois-summary.tex}}
    \label{tab:illinois-summary}
    \justify
    \footnotesize
    \textbf{Note}:
    This table shows the summary statistics for every faculty--year observation in the IBHED data, which represents every faculty member in the Illinois public university system over years 2010--2021.
    The numbers are adjusted to 2021 figures by CPI-U.
    Lecturer is a binary for whether the faculty member is designated as a lecturer in the databse, and similarly for the assistant professors, full professors, and administrative faculty;
    salary refers the sum of base salary and benefits.
    All salary and benefits refers to summary statistics on the salary and benefits, respectively, of all faculty (regardless of position).
\end{table}

>>>>

\begin{table}[H]
    \singlespacing
    \centering
    \caption{IBHED Summary Statistics, Faculty Panel 2010--2021.}
    \makebox[\textwidth][c]{\input{tables/illinois-summary.tex}}
    \label{tab:illinois-summary}
    \justify
    \footnotesize
    \textbf{Note}:
    This table shows the summary statistics for every faculty--year observation in the IBHED data, which represents every faculty member in the Illinois public university system over years 2010--2021.
    The numbers are adjusted to 2021 figures by CPI-U.
    Lecturer is a binary for whether the faculty member is designated as a lecturer in the databse, and similarly for the assistant professors, professors, and administrative faculty;
    salary refers the sum of base salary and benefits.
    All salary and benefits refers to summary statistics on the salary and benefits, respectively, of all faculty (regardless of position).
\end{table}

### 2024-09-27 text/sections/09-appendix.tex
Added a number of new things.  2 minor comments to address before sub.
This is all done.

\subsection{IPEDS First Stage}
\label{sec:appendix-ipeds-firststage}

@@

\newpage
\subsection{Illinois IBHED First Stage}
\label{sec:iv-model-indiv}

@@

\begin{table}[h!]
    \singlespacing
    \centering
    \caption{First Stage Estimates, for State Funding by Funding Shift-Share in IBHED Data.}
    \textbf{Panel A: units in \$ per student}

@@

    \label{tab:firststage-illinois}
    \justify
    \footnotesize
    \textbf{Note}:
    These tables show the first stage OLS estimates of regression specification \eqref{eqn:secondstage1_indiv}, showing the effect of the funding shift-share on state funding to gauge performance as an instrument.
    Each observation is a professor-year, in the IBHED data, and funding data are merged from IPEDS.
    %Panel A shows the effect of an funding shift-share of \$-1 per student in the state on the number of \$'s of state funding per student at the university --- i.e.,
    %\$-1 funding shift-share per student in the state leads to \$1.176 less state funding per student at the university according to preferred specification column 1.
    Panel A shows the effect of a $-10$\% change funding shift-share per student in the state on $10$\% change in state funding per student at the university --- i.e.,
    $-10$\% funding shift-share per student in the state leads to $-9.77$\% less state funding per student at the university according to prefferred specification column 1.        
    Standard errors are clustered at the institution-year level, and institution $+$ year fixed effects are included where noted.
\end{table}

@@

    \makebox[\textwidth][c]{
        \begin{tabular}{@{\extracolsep{5pt}}lcccccl} 
            \\[-1.8ex]\hline 
            \hline \\[-1.8ex]
            & First-stage & Lecturers & Asst. Professors & Full Professors & All Faculty & Observations \\ 
            \cline{2-7} 
            \\[-1.8ex]
            \input{tables/facultycount-rawcounts-heterogeneity.tex}
            \\[-1.8ex] \hline 
            \hline 
        \end{tabular}}

@@

    \makebox[\textwidth][c]{
        \begin{tabular}{@{\extracolsep{5pt}}lcccccl} 
            \\[-1.8ex]\hline 
            \hline \\[-1.8ex]
            & First-stage & Lecturers & Asst. Professors & Full Professors & All Faculty & Observations \\ 
            \cline{2-7} 
            \\[-1.8ex]
            \input{tables/facultycount-heterogeneity.tex}
            \\[-1.8ex] \hline 
            \hline 
        \end{tabular}}
    \label{tab:facultycount-heterogeneity}
    \justify
    \footnotesize
    \textbf{Note}:
    These tables show the IV estimates of regression specification \eqref{eqn:secondstage}, 
    in the same manner as \autoref{tab:facultycount-shock-reg}, but restricting to institutions ranked as most selective, selective, and unranked by \cite{barrons2009} --- and including state
    The first column presents the coefficient between state funding and shift-share IV, which is a string first-stage among every level of selectivity for public universities.
    The other columns show the coefficient between state funding the count of faculty per students.
    For example, Row 1 of panel B shows that a $10\%$ cut in the state shift-share leads to a fall of $9.44\%$ in state funding for the public universities ranked as ``most selective.''
    Standard errors for the coefficient estimates are in brackets, and the outcome mean are in square brackets beneath.
\end{table}

@@

\cite{hinrichs2022state} analyses IPEDS data only in the years 2011--2019, as the Department of Education added a number of questions to the IPEDS survey asking how many part- and full-time professors are employed by the university.
This means that they define the shift-share instrument with a base year of 2011, do not adjust for the student population size --- in neither the state nor the university under consideration (i.e., on neither shift nor share):
\begin{align}
    \label{eqn:replication-instrument}
    Z^{2011}_{i,t} &=
    \text{Total State Funding}_{s(i),t} \times
    \left( \frac{\text{State Funding}_{i,2011}}{\text{Total Revenues}_{i,2011}} \right).
\end{align}
I replicate the $Z^{2011}_{i,t}$ formulation of the shift-share instrument, showing it is strong in predicting state funding (without adjusting for student population) in following years 2012--2019.
There are only minor differences in the results presented to that for Table 2 in \cite{hinrichs2022state}, as their estimation is on the sample of universities across different samples.
\autoref{tab:firststage-replicate} replicates this finding on the sample of universities who report faculty counts by rank.
\begin{table}[H]
    \singlespacing
    \centering
    \caption{Replication of First-Stage Estimates, Predicting State Funding by Funding Shift-Share, in IPEDS Data 2012--2019 \citep{hinrichs2022state}.}
    \makebox[\textwidth][c]{\input{tables/firststage-replicate.tex}}
    \label{tab:firststage-replicate}
    \justify
    \footnotesize
    \textbf{Note}:
    These tables show the first stage OLS estimates of regressing state funding in years 2012-2019 but the 2011 base share version of the shift-share instrument, without adjusting for student population size.
    Standard errors are clustered at the state-year level, and university $+$ year fixed effects are included where noted.
    The F statistic is for the excluded instrument (not for overall regression), after accounting for fixed effects and cluster dependence \citep{olea2013robust}.
\end{table}
This definition contrasts with the analysis in \autoref{sec:empirics}, and \cite{NBERw23736}, \cite{NBERw23736}.
All three use a shift-share based in the year 1990, or averaged 1990--1993, analyse outcomes in the 1990s and 2000s, and adjust for student population size.

\begin{table}[H]
    \singlespacing
    \centering
    \caption{Replication of Second-Stage Estimates, Effects of State Funding on Faculty Counts, in IPEDS Data 2012--2019 \citep{hinrichs2022state}.}
    \makebox[\textwidth][c]{\input{tables/facultycount-replicate.tex}}
    \label{tab:facultycount-replicate}
    \justify
    \footnotesize
    \textbf{Note}:
    These tables show the second stage OLS and 2SLS estimates of regression specification \eqref{eqn:secondstage}, using the state funding shift-share based in 2011 (as described above) to instrument for state funding in the columns labelled 2SLS.
    State funding is measured in \$ millions.
    Each observation is a public university-year, in the IPEDS data.
    This shows the effect of a state funding cut of \$$1,000,000$ on the number of faculty --- i.e.,
    a cut of \$$1,000,000$ leads to 0.4 fewer lecturers according to column 2.
    Outcome-mean is the mean of the outcome, the number faculty at the university.
    Standard errors are clustered at the state-year level, and university $+$ year fixed effects are included through-out.
\end{table}

>>>>

\subsection{IPEDS First-Stage}
\label{sec:appendix-ipeds-firststage}

@@

\newpage
\subsection{Illinois IBHED First-Stage}
\label{sec:iv-model-indiv}

@@

\begin{table}[h!]
    \singlespacing
    \centering
    \caption{First-Stage Estimates, for State Funding by Funding Shift-Share in IBHED Data.}
    \textbf{Panel A: units in \$ per student}

@@

    \label{tab:firststage-illinois}
    \justify
    \footnotesize
    \textbf{Note}:
    These tables show the first-stage OLS estimates of regression specification \eqref{eqn:secondstage1_indiv}, showing the effect of the funding shift-share on state funding to gauge performance as an instrument.
    Each observation is a professor-year, in the IBHED data, and funding data are merged from IPEDS.
    %Panel A shows the effect of an funding shift-share of \$-1 per student in the state on the number of \$'s of state funding per student at the university --- i.e.,
    %\$-1 funding shift-share per student in the state leads to \$1.176 less state funding per student at the university according to preferred specification column 1.
    Panel A shows the effect of a $-10$\% change funding shift-share per student in the state on $10$\% change in state funding per student at the university --- i.e.,
    $-10$\% funding shift-share per student in the state leads to $-9.77$\% less state funding per student at the university according to prefferred specification column 1.        
    Standard errors are clustered at the institution-year level, and institution $+$ year fixed effects are included where noted.
\end{table}

@@

    \makebox[\textwidth][c]{
        \begin{tabular}{@{\extracolsep{5pt}}lcccccl} 
            \\[-1.8ex]\hline 
            \hline \\[-1.8ex]
            & First-stage & Lecturers & Asst. Professors & Professors & All Faculty & Observations \\ 
            \cline{2-7} 
            \\[-1.8ex]
            \input{tables/facultycount-rawcounts-heterogeneity.tex}
            \\[-1.8ex] \hline 
            \hline 
        \end{tabular}}

@@

    \makebox[\textwidth][c]{
        \begin{tabular}{@{\extracolsep{5pt}}lcccccl} 
            \\[-1.8ex]\hline 
            \hline \\[-1.8ex]
            & First-stage & Lecturers & Asst. Professors & Professors & All Faculty & Observations \\ 
            \cline{2-7} 
            \\[-1.8ex]
            \input{tables/facultycount-heterogeneity.tex}
            \\[-1.8ex] \hline 
            \hline 
        \end{tabular}}
    \label{tab:facultycount-heterogeneity}
    \justify
    \footnotesize
    \textbf{Note}:
    These tables show the IV estimates of regression specification \eqref{eqn:secondstage}, 
    in the same manner as \autoref{tab:facultycount-shock-reg}, but restricting to institutions ranked as most selective, selective, and unranked by \cite{barrons2009} --- and including state
    The first column presents the coefficient between state funding and shift-share IV, which is a string first-stage among every level of selectivity for public universities.
    The other columns show the coefficient between state funding the count of faculty per students.
    For example, Row 1 of panel B shows that a $10\%$ cut in the state shift-share leads to a fall of $9.44\%$ in state funding for the public universities ranked as ``most selective.''
    Standard errors for the coefficient estimates are in brackets, and the outcome mean are in square brackets beneath.
\end{table}

@@

\cite{hinrichs2022state} analyses IPEDS data only in the years 2011--2019, as the Department of Education added a number of questions to the IPEDS survey asking how many part- and full-time professors are employed by the university.
This means that they define the shift-share instrument with a base year of 2011, do not adjust for the student population size --- in neither the state nor the university under consideration (i.e., on neither shift nor share):
\begin{align}
    \label{eqn:replication-instrument}
    Z^{2011}_{i,t} &=
    \text{Total State Funding}_{s(i),t} \times
    \left( \frac{\text{State Funding}_{i,2011}}{\text{Total Revenues}_{i,2011}} \right).
\end{align}
I replicate the $Z^{2011}_{i,t}$ formulation of the shift-share instrument, showing it is strong in predicting state funding (without adjusting for student population) in following years 2012--2019.
There are only minor differences in the results presented to that for Table 2 in \cite{hinrichs2022state}, as their estimation is on the sample of universities across different samples.
\autoref{tab:firststage-replicate} replicates this finding on the sample of universities who report faculty counts by rank.
\begin{table}[H]
    \singlespacing
    \centering
    \caption{Replication of First-Stage Estimates, Predicting State Funding by Funding Shift-Share, in IPEDS Data 2012--2019 \citep{hinrichs2022state}.}
    \makebox[\textwidth][c]{\input{tables/firststage-replicate.tex}}
    \label{tab:firststage-replicate}
    \justify
    \footnotesize
    \textbf{Note}:
    These tables show the first-stage OLS estimates of regressing state funding in years 2012-2019 but the 2011 base share version of the shift-share instrument, without adjusting for student population size.
    Standard errors are clustered at the state-year level, and university $+$ year fixed effects are included where noted.
    The F statistic is for the excluded instrument (not for overall regression), after accounting for fixed effects and cluster dependence \citep{olea2013robust}.
\end{table}
This definition contrasts with the analysis in \autoref{sec:empirics}, and \cite{NBERw23736,NBERw27885}.
All three use a shift-share based in the year 1990, or averaged 1990--1993, analyse outcomes in the 1990s and 2000s, and adjust for student population size.

\begin{table}[H]
    \singlespacing
    \centering
    \caption{Replication of IV Estimates, Effects of State Funding on Faculty Counts, in IPEDS Data 2012--2019 \citep{hinrichs2022state}.}
    \makebox[\textwidth][c]{\input{tables/facultycount-replicate.tex}}
    \label{tab:facultycount-replicate}
    \justify
    \footnotesize
    \textbf{Note}:
    These tables show the second stage OLS and 2SLS estimates of regression specification \eqref{eqn:secondstage}, using the state funding shift-share based in 2011 (as described above) to instrument for state funding in the columns labelled 2SLS.
    State funding is measured in \$ millions.
    Each observation is a public university-year, in the IPEDS data.
    This shows the effect of a state funding cut of \$$1,000,000$ on the number of faculty --- i.e.,
    a cut of \$$1,000,000$ leads to 0.4 fewer lecturers according to column 2.
    Outcome-mean is the mean of the outcome, the number faculty at the university.
    Standard errors are clustered at the state-year level, and university $+$ year fixed effects are included through-out.
\end{table}
